Intrinsic Verification of Parsers and Formal Grammar Theory in Dependent Lambek Calculus

### 2024-10-31 paper/paper.tex
turing machine wip

\subsection{UnReStRiCtEd}
%% 5. Expressiveness: Turing Machines

>>>>

\subsection{Unrestricted Grammars}
%% 5. Expressiveness: Turing Machines
The expressive power of \theoryabbv spans the entire Chomsky hierachy, as we may
encode the grammars accepted by Turing machines.

We nonlinearly encode the tape of the Turing machine as
function from $\mathbb{Z} \to \Gamma$, where $\Gamma$ is your tape alphabet. The
grammar of traces for a Turing machine linear consumes the input string and
writes it to the tape. From here, we nonlinear reason about machine transitions.
We execute the machine and track its current state as part of the nonlinear
indexing data.
